Hydras \& Co.

### 2024-02-07 doc/chapter-primrec.tex
minor changes in pdf doc

\subsubsection{The constant function of value 0}
\label{sect:k0}

The \emph{unary} function which always returns $0$ may be defined through the \emph{composition} construction (with $n=1$, $m=0$, and $h=\texttt{zero}$).

% If we consider any value of $n$, the same construction
% builds the constant function of type $\mathbb{N}^n \arrow \mathbb{N}$ which returns $0$.

\subsubsection{Constant functions}

Let $k$ be some natural number; the unary constant function which always returns $k$ is built through $k$ nested compositions of the 
successor function with the  unary constant function which returns $0$.

@@

Module \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec} defines and export  the notation ``\texttt{$f$ =x= $g$}'' for ``\texttt{extEqual $n$ $f$ $g$}'' \footnote{in parsing mode, provided $f$ has explicitely the type (\texttt{naryFunc $n$}).}

@@

Inhabitants of type (\texttt{PrimRec $n$}) are not \coq{} functions like \texttt{Nat.mul}, or \texttt{Arith.Factorial.fact}, etc. but terms of an abstract syntax for the language of primitive recursive functions. The bridge between this language and the word of usual functions
is an interpretation function (\texttt{evalprimRec $n$})  of type
$\texttt{PrimRec}\,n \rightarrow  \texttt{naryFunc}\,n$.
This function is defined by mutual recursion,  together with the  function 
(\texttt{evalprimRecS $n$ $m$}) of type 
($\texttt{PrimRecs}\,n\,m \rightarrow  \texttt{Vector.t}\,(\texttt{naryFunc}\,n)\,m$).

>>>>

\subsubsection{Constant functions}
\label{sect:k0}

The \emph{nullary} constant function which returns $0$ is
simply the \texttt{zero} construction.

If we want to consider the \emph{unary} function which
maps any natural number $i$ to $0$, we may built it
through the \emph{composition} construction, instanciated
with $n=1$, $m=0$, and $h=\texttt{zero}$.

\begin{exercise}
Let $m$ and $k$ be two natural numbers; please build the primitive recursive function which maps any
tuple $t\in \mathbb{N}^m$ to $k$.
\end{exercise}

@@

Module \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec} defines and export  the notation ``\texttt{$f$ =x= $g$}'' for ``\texttt{extEqual $n$ $f$ $g$}'' \footnote{in parsing mode, the provided $f$ should be explicitely typed as  (\texttt{naryFunc $n$}).}

\vspace{6pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}}

@@

Inhabitants of type (\texttt{PrimRec $n$}) are not \coq{} functions like \texttt{Nat.mul}, \linebreak \texttt{Arith.Factorial.fact}, etc. but terms of an abstract syntax for the language of primitive recursive functions. The bridge between this language and the word of usual functions
is an interpretation function (\texttt{evalprimRec $n$})  of type
$\texttt{PrimRec}\,n \rightarrow  \texttt{naryFunc}\,n$.
This function is defined by mutual recursion,  together with the  function 
(\texttt{evalprimRecS $n$ $m$}) of type \linebreak
($\texttt{PrimRecs}\,n\,m \rightarrow  \texttt{Vector.t}\,(\texttt{naryFunc}\,n)\,m$).
